What Can Stack Traces Tell us about the Use of Exceptions in Java?

### 2014-05-09 android-stacks.tex
Minor header fixes
Stack wrappings only histogram

%commented only for submission:
We could observe in this study that the NullPointerException and other
other implicitly signaled exceptions represented most of the exceptions reported
on issues in both Java and Android subset. For such exceptions, which represent
programming bugs or resource limitations, there is usually no proper handling
besides presenting an error message to the user and restarting the application -
only high fault tolerant systems need to provide solutions to handle them.

@@

\subsection{Direct instances of RuntimeExceptions been thrown.}

@@

\subsection{Undocumente runtime exceptions been thrown.}

@@

\begin{figure}
  \begin{center}
    \includegraphics[scale=0.5]{only-wrap-histogram.pdf}
  \end{center}
  \caption{Number of  stack traces wrappings for Java and Android repositories. }
  \label{fig:sizewrapbhists}
\end{figure}

IMPORTANT:  ~\todo{We need to update this data because it is still including PulWifi. Gerogios I sent the filtered data to you by email, and saved on file java-new-stack-sizes.csv in this repository.}

>>>>

We could observe in this study that the NullPointerException and other
other implicitly signaled exceptions represented most of the exceptions reported
on issues in both Java and Android subset. For such exceptions, which represent
programming bugs or resource limitations, there is usually no proper handling
besides presenting an error message to the user and restarting the application -
only high fault tolerant systems need to provide solutions to handle them.

@@

\subsection{Direct instances of RuntimeExceptions being thrown.}

@@

\subsection{Undocumented runtime exceptions being thrown.}

@@

\begin{figure}
  \begin{center}
    \includegraphics[scale=0.5]{stack-wrappings-hist.pdf}
  \end{center}
  \caption{Number of stack traces wrappings for Java and Android repositories. }
  \label{fig:sizewrapbhists}
\end{figure}
